Computer Science House Constitution

### 2025-05-19 constitution.tex
Updated Section 9.A.2.A and 9.A.2.B in accordance with NY law

Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.
\asubsubsection{Expectations of Voting Members}
\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue (e.g., not on co-op).

@@

\asubsubsection{§ 120.16 Hazing in the first degree.}
A person is guilty of hazing in the first degree when, in the course of another person's initiation into or affiliation with any organization, he intentionally or recklessly engages in conduct which creates a substantial risk of physical injury to such other person or a third person and thereby causes such injury.
Hazing in the first degree is a class A misdemeanor.

\asubsubsection{§ 120.17 Hazing in the second degree.}
A person is guilty of hazing in the second degree when, in the course of another person's initiation or affiliation with any organization, he intentionally or recklessly engages in conduct which creates a substantial risk of physical injury to such other person or a third person.
Hazing in the second degree is a violation.

>>>>

\asubsubsection{Expectations of Voting Members}
\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.

@@

\asubsubsection{§ 120.16 Hazing in the first degree.}
A person is guilty of hazing in the first degree when, in the course of another person's initiation into or affiliation with any organization, he intentionally or recklessly engages in conduct, including, but not limited to, making physical contact with or requiring physical activity of such other person, which creates a substantial risk of physical injury to such other person or a third person and thereby causes such injury.
Hazing in the first degree is a class A misdemeanor.

\asubsubsection{§ 120.17 Hazing in the second degree.}
A person is guilty of hazing in the second degree when, in the course of another person's initiation or affiliation with any organization, he intentionally or recklessly engages in conduct, including, but not limited to, making physical contact with or requiring physical activity of such other person, which creates a substantial risk of physical injury to such other person or a third person.
Hazing in the second degree is a violation.
